Caveat Emptor: light curves of the brightest stars in the \\ Southern sky as seen by bRing

### 2023-09-27 src/tex/ms.tex
[showyourwork] overleaf sync

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/del_Pav_thesis.png}
    \caption{Light curve of delta Pavonis after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of delta Pavonis is 2424942.}
    \label{del_Pav}
\end{figure}

>>>>

% \begin{figure}
%     \centering
%     \includegraphics[width=\linewidth]{figures/del_Pav_thesis.png}
%     \caption{Light curve of delta Pavonis after data reduction and detrending. The time is displayed on the horizontal axis in Julian Date and the apparent magnitude is displayed on the vertical axis. The ASCC-number of delta Pavonis is 2424942.}
%     \label{del_Pav}
% \end{figure}
